Equalizer Programming Guide\\ {\vspace{-1ex}\footnotesize\sffamily\mdseries \htmladdnormallink{http://www.equalizergraphics.com/documents/Developer/ProgrammingGuide.pdf} {http://www.equalizergraphics.com/documents/ProgrammingGuide.pdf}}

### 2007-10-21 Developer/ProgrammingGuide/paper.tex
Update Programming Guide
[ ] May break build
[ ] Breaks existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

\title{Equalizer Programming Guide\\
  {\footnotesize\sffamily\mdseries
    \htmladdnormallink{http://www.equalizergraphics.com/documents/Developer/ProgrammingGuide.pdf}
    {http://www.equalizergraphics.com/documents/ProgrammingGuide.pdf}}
}
\author{Stefan Eilemann\\{\footnotesize Eyescale Software GmbH}
}
\date{
  \vspace{4cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
  \textbf{DRAFT}\\[\medskipamount]
  Version 0.9.2 for Equalizer v0.4\\[\medskipamount]
  \today
}

@@

\clearpage
\tableofcontents
\thispagestyle{empty}
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    0.9.2   & Oct 19, 2007 & Jonas' feedback, changes related to
                             per-node frame sync\\
    0.9.1   & Oct 8,  2007 & review pass\\
    0.9     & Oct 7,  2007 & add eqHello, draft assembly in eVolve\\
    0.8     & Sep 28, 2007 & add head tracking, finish channel,
                             proof-reading pass\\
    0.7     & Sep 21, 2007 & start channel and image compositing,
                             add event handling, move to new eqPly
                             code base\\
    0.6     & Sep 14, 2007 & add pipe, window and object manager\\
    0.5     & Sep 3,  2007 & add config and partly pipe\\
    0.4     & Aug 31, 2007 & add distributed objects\\
    0.3     & Aug 26, 2007 & add application and render client\\
    0.2     & Aug 20, 2007 & add main function\\
    0.1     & Aug 19, 2007 & outline the basic concepts\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

Equalizer provides a framework for the development of parallel
OpenGL\texttrademark\ applications. Equalizer-based applications can run
a single shared-memory system with multiple graphics cards (GPU's) or on
graphics clusters. This Programming Guide introduces the programming
interface using the \textsf{eqPly} example shipped with Equalizer as a
guideline.

Equalizer is the next step in the evolution of generic parallel programming
interfaces for visualization applications using OpenGL. Existing
% rephrase ( aber ich weiss auch nicht wie :) )
solutions, such as SGI's OpenGL Multipipe\texttrademark\ SDK, VRCO's
Cavelib\texttrademark\ and VRJuggler, implement a subset of concepts
similar to Equalizer. In other areas, e.g., tracking device support,
they provide more functionality.

@@

\fig{fConfig} shows one example configuration for a four-side
CAVE\texttrademark, running on two machines (nodes) using three graphics
cards (pipes) with one window each to render to the four output channels
connected to the projectors for each of the walls. The compound
description is only used by the server to compute the rendering
tasks. The application is not aware of compounds, and does not need to
concern itself with the parallel rendering logics of a configuration.

@@

{\footnotesize\begin{lstlisting}
void InitData::getInstanceData( eqNet::DataOStream& os )
{
    os << _frameDataID << _windowSystem << _useVBOs << _useShaders << _filename;
}

void InitData::applyInstanceData( eqNet::DataIStream& is )
{
    is >> _frameDataID >> _windowSystem >> _useVBOs >> _useShaders >> _filename;

>>>>

\title{Equalizer Programming Guide\\
  {\vspace{-1ex}\footnotesize\sffamily\mdseries
    \htmladdnormallink{http://www.equalizergraphics.com/documents/Developer/ProgrammingGuide.pdf}
    {http://www.equalizergraphics.com/documents/ProgrammingGuide.pdf}}
}
\author{Eyescale Software GmbH}

\date{
  \vspace{4cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
  \textbf{DRAFT}\\[\medskipamount]
  Version 0.9.3 for Equalizer 0.4\\[\medskipamount]
  \today
}

@@

\clearpage

\thispagestyle{empty}
\section*{Equalizer 0.4 Programming Guide}
\subsection*{Contributors}

Written by Stefan Eilemann.\\
Engineering contributions by Maxim Makhinya and Jonas B\"osch.

\subsection*{Copyright}

\textcopyright 2007 Eyescale Software GmbH. All rights reserved. No
permission is granted to copy, distribute, or create derivative works
from the contents of this electronic documentation in any manner, in
whole or in part, without the prior written permission of Eyescale
Software GmbH.

\subsection*{Trademarks and Attributions}

OpenGL is a registered trademark, OpenGL Multipipe is a trademark of
Silicon Graphics, Inc. Linux is a registered trademark of Linus
Torvalds. CAVELib is a registered trademark of the University of
Illinois. The CAVE is a registered trademark of the Board of Trustees of
the University of Illinois at Chicago. All other trademarks and
copyrights herein are the property of their respective owners.

\subsection*{Feedback}

If you have comments about the content, accuracy or comprehensibility of
this programming guide, please contact
\htmladdnormallink{eile@equalizergraphics.com}
{mailto:eile@equalizergraphics.com?subject=Equalizer\%20Programming\%20Guide}.

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    0.9.3   & Oct 21, 2007 & update title page, add front matter\\
    0.9.2   & Oct 19, 2007 & Jonas' feedback, changes related to
                             per-node frame sync\\
    0.9.1   & Oct 8,  2007 & review pass\\
    0.9     & Oct 7,  2007 & add eqHello, draft assembly in eVolve\\
    0.8     & Sep 28, 2007 & add head tracking, finish channel,
                             proof-reading pass\\
    0.7     & Sep 21, 2007 & start channel and image compositing,
                             add event handling, move to new eqPly
                             code base\\
    0.6     & Sep 14, 2007 & add pipe, window and object manager\\
    0.5     & Sep 3,  2007 & add config and partly pipe\\
    0.4     & Aug 31, 2007 & add distributed objects\\
    0.3     & Aug 26, 2007 & add application and render client\\
    0.2     & Aug 20, 2007 & add main function\\
    0.1     & Aug 19, 2007 & outline the basic concepts\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

Equalizer provides a framework for the development of parallel OpenGL
applications. Equalizer-based applications can run a single
shared-memory system with multiple graphics cards (GPU's) or on graphics
clusters. This Programming Guide introduces the programming interface
using the \textsf{eqPly} example shipped with Equalizer as a guideline.

Equalizer is the next step in the evolution of generic parallel programming
interfaces for visualization applications using OpenGL. Existing
% rephrase ( aber ich weiss auch nicht wie :) )
solutions, such as OpenGL Multipipe SDK, Cavelib and VRJuggler,
implement a subset of concepts similar to Equalizer. In other areas,
e.g., tracking device support, they provide more functionality.

@@

\fig{fConfig} shows one example configuration for a four-side
CAVE, running on two machines (nodes) using three graphics
cards (pipes) with one window each to render to the four output channels
connected to the projectors for each of the walls. The compound
description is only used by the server to compute the rendering
tasks. The application is not aware of compounds, and does not need to
concern itself with the parallel rendering logics of a configuration.

@@

{\footnotesize\begin{lstlisting}
void InitData::getInstanceData( eqNet::DataOStream& os )
{
    os << _frameDataID << _windowSystem << _precision << _brightness << _useGLSL
       << _filename;
}

void InitData::applyInstanceData( eqNet::DataIStream& is )
{
    is >> _frameDataID >> _windowSystem >> _precision >> _brightness >> _useGLSL
       >> _filename;
